---
title: "Super_trashy_documentazione_solo_per_ mieI_occhie"
author: "Andrea Brancaccio"
date: "`r Sys.Date()`"
output:
    bookdown::html_document2:
        toc: yes
        toc_float: yes
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
source("Shapes_list-10-11-Ottavia.R")
source("Class and Methods v02.R")
source("Rules_27102022.R")
```

# Methods applicable to field object
- `cof()`
- `decof()`
- `hide()`
- `show()`
- `replace()`
- `draw()`

# COF (Guarda l'altra doumentazione)

# DECOF 
Function `decof()` want in input a single object field obtained by the concatenation of
many *single* field (e.g., `square4()`, `lily()`). The outcome is a list containting 
the basic elements that were used to compose the field. For instance, `decof(square4())` 
return a list containing four field corresponding with the four lines `vline()`,`vline()`,
`hline()` and `hline()`.

Example 1!

```{r echo=TRUE}
example<-cof(square(),triangle(),luck())
x<-decof(example)
length(x)
x[[1]]$shape
x[[2]]$shape
x[[3]]$shape
```
If there is not enough information for reconstruct the original `$shape` of the basic elements,
the field will be filled by default with `token`.

Example 2!

```{r echo=TRUE}
x<-decof(s.lily())
length(x)
x[[1]]$shape
x[[2]]$shape ##etc
```

# HIDE \& SHOW

Functions `hide()` and `show()` are two sides of the same coin. 
They require in input a field `object` and a vector of `index`.
`index` refers to the relative position of the basic elements that compose the matrix.

Function `hide()` change the field `$visible` of all the indexed to a **0** 
no matter what was initial value.

```{r echo=TRUE}
example<-cof(square(),triangle(),luck())
example$visible 
example<-hide(example,c(1,3))## hide the square and the luck
example$visible
example<-hide(example) ## hide everything
example$visible
```

Function `show()` change the field `$visible` of all the indexed to a **1** 
no matter what was initial value.

```{r echo=TRUE}
example<-hide(cof(square(),triangle(),luck()))
example$visible 
example<-show(example,c(2,3))## show the triangle and the luck
example$visible
example<-show(example) ## show everything
example$visible
```


# REPLACE

Functions `replace()` substitute a basic field in an object with another basic field.
It require in input 

1. `obj` a compose field (e.g.,`square4()`)

2. `index` of the element in `obj` to replace

3. `obj2` new object to substitute the previous one

EXAMPLE !
```{r echo=TRUE}
example<-cof(square(),triangle(),luck())
example$shape
example<-replace(example,2,circle()) ##replacing the triangle with the circle
example$shape
```